\textbf{Sugarlike: A Language Identification Library for Low Resource Languages}

### 2013-11-05 sugarlike.tex
Solve latex layout issues.

\begin{itemize}
\item Universal Declaration of Human Rights: almost parallel data,  needs some cleaning (\~300 languages)
\item Language Id Corpus (LId): character 3-grams of Crúbadán corpus %there's some unknown angeled brackets
\item Crawl the tweets linked to www.indigenoustweets.com (\~150 languages)
\item Crawl the blogs linked to www.indigenoustweets.com/blogs (\~75 languages)
\end{itemize}

@@

\
\
\
\
\

\bibliography{literature.bib}{}
\bibliographystyle{plain}

>>>>

\begin{itemize}
\item Universal Declaration of Human Rights: almost parallel data,  needs some cleaning ($\sim$300 languages)
\item Language Id Corpus (LId): character 3-grams of Crúbadán corpus %there's some unknown angeled brackets
\item Crawl the tweets linked to www.indigenoustweets.com ($\sim$150 languages)
\item Crawl the blogs linked to www.indigenoustweets.com/blogs ($\sim$75 languages)
\end{itemize}

@@

\
\\
\
\\

\bibliography{literature}{}
\bibliographystyle{plain}
